Supplementary Information: Vulnerability of tree growth

### 2024-07-10 doc/manuscript.Rmd
update methods for calculating resistance

*Resistance*
-Dendrometer band measurements - census protocol
-Calculated DBH at each instance from first DBH and window size using Condit's functions.
-Removed measures with large decimal errors, large outliers (> 3 SD). 
- For all individuals with three points of measurements for each drought, calculated raw increment as difference between relevant censuses to get pre-drought increment and drought-year increment.
- Resistance - difference between pre-drought and drought-year increment

*Tree size*
- calculated DBH for at the start of the pre-drought year from dendrometer band window

>>>>

*Resistance*
- Dendrometer band measurements - census protocol
- Calculated DBH at each instance from first DBH and window size using Condit's functions.
- Removed measures with large decimal errors, potential band misID, large outliers (> 3 SD). 
- calculated increments for each individual for each census year using dendroband data and tape measurement
- tape measurement does not have accuracy required to measure this effect, but used tape increments to detect outliers.
- removed all increment measurements with more than 0.5 cm deviation from the 1:1 line for dendro and tape increments 
- For each drought year, used drought-year increment.
- for each tree, long-term growth was calculated as the mean growth across 20 years of full-plot censuses
- Resistance - ratio of drought-year increment to long-term growth for each individual tree

*Tree size*
- calculated DBH for at the start of the drought year from dendrometer band window
